### 2017-04-03 paper/sections/Formalization.tex
Fix.

\begin{figure*}[htbp]
	\begin{mathpar}
	\inferrule* [left=]
		{  \mostSpecific(m, I_d, I_s) = \{I\} \\
			\mostSpecific_3(m, I_d, I) = \{J\} \\
			\kwinterface \; J \; \kwextends \; \overline{J} \; \{\method{I_E}{m}{I_X}{x}{I}{e_0}\ldots\}}
		{\mbody(m, I_d, I_s) = (\overline{I_X} \; \overline{x}, I_E \; e_0)}

	\inferrule* [left=]
	{ set = \; \{ K <: J \; $and$ \; K >: I \; | \; m \in \updateSet(K, K) \} }
	{\mostSpecific(m, I, J) = \left\{{\begin{tabular}{ll}
				$prune(set)$ & if $set$ is not empty \\ $\mostSpecific_2(m, J)$ & otherwise
			\end{tabular}}\right.}
	\inferrule* [left=]
		{ set = \; \{ K >: I \; | \; m \in \updateSet(K, K) \} }
		{\mostSpecific_2(m, I) = prune(set)}

	\inferrule* [left=]
		{ set = \; \{ K <: J \; $and$ \; K >: I \; | \;
			m \in \updateSet(K, J)  \} }
		{\mostSpecific_3(m, I, J) = prune(set)}

>>>>

\begin{figure*}[htbp]
	\begin{mathpar}
	\inferrule* [left=]
		{  \mostSpecific(m, I_d, I_s) = \{I\} \\
			\mostSpecific_2(m, I_d, I) = \{J\} \\
			\kwinterface \; J \; \kwextends \; \overline{J} \; \{\method{I_E}{m}{I_X}{x}{I}{e_0}\ldots\}}
		{\mbody(m, I_d, I_s) = (\overline{I_X} \; \overline{x}, I_E \; e_0)}

	\inferrule* [left=]
	{ set1 = \; \{ K <: J \; $and$ \; K >: I \; | \; m \in \updateSet(K, K) \} \\
		set2 = \; \{ K >: J \; | \; m \in \updateSet(K, K) \} }
	{\mostSpecific(m, I, J) = \left\{{\begin{tabular}{ll}
				$prune(set1)$ & if $set1$ is not empty \\ $prune(set2)$ & otherwise
			\end{tabular}}\right.}

	\inferrule* [left=]
		{ set = \; \{ K <: J \; $and$ \; K >: I \; | \;
			m \in \updateSet(K, J)  \} }
		{\mostSpecific_2(m, I, J) = prune(set)}
